---
title: "Module_15_Challenge"
author: "K.Engle"
date: "1/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the dplyr library
```{r cars}
library(dplyr)
```

Import and read the MechaCar_mpg.csv file
```{r}
mechacar_df <- read.csv(file = '../MechaCar_mpg.csv')
```

Perform linear regression using the lm() function
```{r}
lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = mechacar_df)
```

```{r}
summary(lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD, data = mechacar_df))
```

Deliverable 2

Import and read the Suspension_Coil file
```{r}
suspen_coil_df <- read.csv(file= '../Suspension_Coil.csv', stringsAsFactors = F)
```

Create a Total_Summary dataframe using the summarize function
```{r}
total_summary <- suspen_coil_df %>% summarize(Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI), .groups= 'keep')
total_summary
```
Create a lot_summary dataframe using the groupby and summarize function to group by Manf lot
```{r}
lot_summary <- suspen_coil_df %>% group_by(Manufacturing_Lot) %>%  summarize(Mean = mean(PSI), Median = median(PSI), Variance = var(PSI), SD = sd(PSI), .groups= 'keep')
lot_summary
```

Deliverable 3

Conduct a test to determine if the PSI across all lots is statistically different from the population mean of 1500 PSI
```{r}
t.test(suspen_coil_df$PSI, mu=1500)
```

```{r}
t.test(subset(suspen_coil_df$PSI, suspen_coil_df$Manufacturing_Lot=="Lot1"), mu=1500)
```

```{r}
t.test(subset(suspen_coil_df$PSI, suspen_coil_df$Manufacturing_Lot=="Lot2"), mu=1500)
```
```{r}
t.test(subset(suspen_coil_df$PSI, suspen_coil_df$Manufacturing_Lot=="Lot3"), mu=1500)
```


